% !TEX program = xelatex

\documentclass{resume}
\usepackage{comment}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Jinhui Shen}

\basicInfo{
  \email{j72shen@edu.uwaterloo.ca} \textperiodcentered\ 
  \phone{6479377982} \textperiodcentered\ 
 \github[github.com/TheaaaShen]{}
  }
\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Java Spring, C++, SQL
  \item Architectures: OOP, CQRS, Event Sourcing, RESTful API, CRUD, Microservices
  \item Others: Linux, IntelliJ, Git, Postman, Docker, JPA, Hibernate
\end{itemize}

\section{\faUsers\ Experiences}

\datedsubsection{\textbf{Software Engineer}}{Jan. 2019 - Apr. 2019}
\datedsubsection{\textit{Autonomic - Transportation as a Service Team}}{Toronto, Canada}
Used Java to deploy Spring microservices to Kubernetes on AWS
\begin{itemize}
  \item Deployed several microservices with CQRS design and Event Sourcing
  \item Wrote Java Spring code to interact with messages from live vehicle data via Kafka streams
  \item Experienced with Extreme Programming and Pair Programming
\end{itemize}

\datedsubsection{\textbf{Associate Programmer Analyst}}{Jan. 2018 - Apr. 2018}
\datedsubsection{\textit{Scotiabank - Risk Management Information Technology Team}}{Toronto, Canada}
Used Python and Java to support internal regulatory reporting system 
\begin{itemize}
  \item Automated the process of fetching reports using Java 
  \item Regulatory project management using JIRA and Leankit
\end{itemize}

\datedsubsection{\textbf{Software Developer Intern}}{May 2017 - Aug. 2017}
\datedsubsection{\textit{Chinese Academy of Sciences - Institute of Computing Technology}}{Beijing, China}
Used Java to optimize the algorithm for Glycan Structure Identification Software (GIPS)
\begin{itemize}
  \item Rewrote and optimized the core data structure and algorithm for the software 
  \item Reduced time consumption to 0.002\%, from 117.87s to 0.0029s
  \item Reduced memory consumption to 2.048\%. from 1763 Mb to 36.1 Mb
\end{itemize}

\section{\faStar\ Projects}

\datedsubsection{\textbf{Hotel Management}}{Sept. 2019 - Present}
\role{Individual Project}{}
A Restful CRUD application using Java Spring and MySQL that manages room information for a hotel
\begin{itemize}
  \item Implemented basic create, read, update, delete features that can be accessed through Postman
  \item Database is built with MySQL, JPA and Hibernate
\end{itemize}

\datedsubsection{\textbf{Quadris}}{Nov. 2017 - Dec. 2017}
\role{Course Project}{}
Implemented object-oriented command-line Tetris game with 5 difficulty levels with C++
\begin{itemize}
  \item Utilized Subject Observer design pattern and Visitor design pattern
  \item Implemented visualization through XWindows
\end{itemize}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{University of Waterloo}}{Sept. 2016 -- Present}
Candidate for Bachelor of Computer Science (Software Engineering Option)
\datedsubsection{\textbf{Wilfrid Laurier University}}{Sept. 2016 -- Present}
Candidate for Bachelor of Business Administration (Marketing Concentration)

\begin{comment}
\section{\faHeartO\ Activities and Awards}
\begin{itemize}[parsep=0.5ex]
  \item Hack the North 2017 Participant
  \item University of Waterloo President’s Scholarship of Distinction
  \item Euclid Mathematics Competition Scholarship
\end{itemize}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
%  \item Website: 
  \item Languages: English - Fluent, Mandarin - Native speaker, Korean -  fluent
\end{itemize}

\end{comment}
\end{document}
